Lyman-$\alpha$ photons through rotating outflows

### 2018-03-30 paper/paper.tex
edit

Finally, the thick gray line correspods to the pure outflow solution
with the Doppler boost added to model rotation's influence.
At $\tauh=10^6$ the Doppler boost does a good job at capturing the broad
morphological features introduced by rotation: the angle dependence,
the broadening and the intensity increase at the line's center.

@@

@@

This shows that the DS model can reproduce the main characteristics of the
RT one. Because of this, we can introduce rotation effects in any spectra
without running the radiative transfer simulations, that usually take a
significant amount of time and computational resources.

In addition to this, we also evaluate the effects of the viewing angle
for fixed rotational and outflows velocity. We measure the intensity of the
valley between peaks, for each $\theta$ and \tauh. Figure \ref{fig:valley_intensity}
summarizes the information with all plots corresponding to the same outflow
velocity of $\vout=5$\kms and rotation velocity of $\vrot=100$\kms.

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
\begin{center}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. Also, the higher \tauh, the better is the fit RT-DS.
		We fixed $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

>>>>

The thick gray line correspods to the pure outflow solution
with the Doppler boost added to model rotation's influence.
At $\tauh=10^6$ the Doppler boost does a good job at capturing the broad
morphological features introduced by rotation: the angle dependence,
the broadening and the intensity increase at the line's center.

@@

Figure \ref{fig:skewness} presente the skwewness results for all the
models together with the DS comparison.

@@

\begin{figure*}
\begin{center}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.28\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. Also, the higher \tauh, the better is the fit RT-DS.
		We fixed $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}
